---
title: "readme"
author: "KwH Kim"
date: "2018년 10월 17일"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

repository name = **ggplot2-book**

branch name = **html**

Here is the code for installing packages. You need to install at least these pakcages.
```{r pack, eval=F}
# dependencies
install.packages('maps')
install.packages('directlabels')
install.packages('sf')
install.packages('USAboundariesData', 
                 repos='http://packages.ropensci.org', 
                 type = 'source')
install.packages('wesanderson')
install.packages('mapproj')
install.packages('ggthemes')
install.packages('Lahman')
```

```{r chapterNames, message=F}
i.chpter = 1
chpName = c('Introduction', 
            'Getting started with ggplot2',
            'Toolbox',
            'Mastering the grammar',
            'Build a plot layer by layer',
            'Scales, axes and legends',
            'Positioning',
            'Themes',
            'Data Analysis',
            'Data transformation',
            'Modelling for visualization',
            'Programming with ggplot2')
files = c('introduction', 'ggplot', 'toolbox', 
          'mastery', 'layers', 'scales', 
          'position', 'themes', 'data-manip', 
          'tidy-data', 'modelling', 'programming')
```


## Contents
|no   |name   |rmd   |html |
|---|---|---|---|
|`r i.chpter`  |`r chpName[i.chpter]`   |`r file.exists(paste0(files[i.chpter],'.rmd'))`   |`r file.exists(paste0(files[i.chpter],'.html'))` `r i.chpter = i.chpter+1`|
|`r i.chpter`  |`r chpName[i.chpter]`   |`r file.exists(paste0(files[i.chpter],'.rmd'))`   |`r file.exists(paste0(files[i.chpter],'.html'))` `r i.chpter = i.chpter+1`| 
|`r i.chpter`  |`r chpName[i.chpter]`   |`r file.exists(paste0(files[i.chpter],'.rmd'))`   |`r file.exists(paste0(files[i.chpter],'.html'))` `r i.chpter = i.chpter+1`| 
|`r i.chpter`  |`r chpName[i.chpter]`   |`r file.exists(paste0(files[i.chpter],'.rmd'))`   |`r file.exists(paste0(files[i.chpter],'.html'))` `r i.chpter = i.chpter+1`| 
|`r i.chpter`  |`r chpName[i.chpter]`   |`r file.exists(paste0(files[i.chpter],'.rmd'))`   |`r file.exists(paste0(files[i.chpter],'.html'))` `r i.chpter = i.chpter+1`| 
|`r i.chpter`  |`r chpName[i.chpter]`   |`r file.exists(paste0(files[i.chpter],'.rmd'))`   |`r file.exists(paste0(files[i.chpter],'.html'))` `r i.chpter = i.chpter+1`| 
|`r i.chpter`  |`r chpName[i.chpter]`   |`r file.exists(paste0(files[i.chpter],'.rmd'))`   |`r file.exists(paste0(files[i.chpter],'.html'))` `r i.chpter = i.chpter+1`| 
|`r i.chpter`  |`r chpName[i.chpter]`   |`r file.exists(paste0(files[i.chpter],'.rmd'))`   |`r file.exists(paste0(files[i.chpter],'.html'))` `r i.chpter = i.chpter+1`| 

Trying to render `.html`

```{r rmdRender, error=T}
library(rmarkdown)

for (i in seq_along(files)) {
  if (!file.exists(paste0(files[i],'.html'))) {
    cat(paste('Rendering ', paste0(files[i],'.html')), '\n')
    rmarkdown::render(paste0(files[i],'.rmd'))
  }
}
```




